---
title: "Day Night Delay Analysis Script"
author: Jade Yonehiro
output:
  html_document:
    theme: cosmo
    highlight: breezedark
    toc: true
    toc_float: true
    toc_depth: 2
    code_download: true
---
Analyses for the paper: Wait! Does Imposing Delays Improve Children's Inhibitory Control?  
Authors: Jade Yonehiro, Jane Barker, Anne Roche and Yuko Munakata  
Contact: Jnyonehiro@ucdavis.edu  

# Set up
```{r message=FALSE, warning=FALSE}
#read in file
library(knitr)
library(kableExtra)
library(tidyverse)
library(dplyr)
library(yarrr)
library (ggplot2)
library(lmSupport)
library(lme4)
library(lmerTest)
library(car)         # Needed for McSummary()
library(moments)     # Needed for skewness() and kurtosis() 
source('http://psych.colorado.edu/~jclab/R/mcSummaryLm.R')

#Read in data set
finsamp <- read.csv("C:/Users/Jade/Dropbox/0_Studies/6_DayNight_2020/DN_Final_2020.csv")
# Read in variable codebook
codebook <- read.csv("C:/Users/Jade/Dropbox/0_Studies/6_DayNight_2020/DNCodeBook.csv")

#Create html table to display codebook
codebook %>%
  kbl() %>%
  kable_styling()

#Fix variables to be in correct format
finsamp<-finsamp%>%
  mutate(AgeDays = as.numeric(AgeDays),         # Make age numeric
         DNCondition = as.factor(DNCondition),  # Make condition a factor
         # Set up contrasts
         DNCondition = ifelse(DNCondition == "BETWEEN",0,              # Between = ditty between trials (control condition)
                              ifelse(DNCondition == "WITHIN",1,NA)))   # within = ditty within trials (delay condition) 
```


## Age-restricted sample: 3.5 year cutoff  
Children were recruited from a database of families who had volunteered to participate as part of a larger study with additional measures targeting children aged 3.0 - 5.0 years. 59 of the children in the total sample fell outside of the a priori target age range of the current study (3.5-5.0 years) and were not included. 
```{r}
dnsamp <- subset(finsamp, AgeYears >=3.5)       # Restrict sample to 3.5+ 
```


## Correlation across coders
- Correlation between X and Y = 0.987 for the final data set. Coder Y did not code the full data set (only 32/68 total participants).
- Take mean scores across coders to calculate total correct trials
```{r}
#Get correlation
cor.test(dnsamp$TotCorr.y,dnsamp$TotCorr.x)     #.98 for this subset

#Get mean score across coders
dnsamp$FinCorrect <- rowMeans(dnsamp[c("TotCorr.y","TotCorr.x")], na.rm=TRUE) 
```

# Assumptions checks
```{r}
#Check distribution: they are highly skewed
#hist(dnsamp$FinCorrect)
skewness(dnsamp$FinCorrect) #These data are heavily negatively skewed
kurtosis(dnsamp$FinCorrect) #These data are leptokurtic (peak at mean)

# Square responses
dnsamp$Fin2 <- ((dnsamp$FinCorrect)^2)        # Squared is the better solution
#hist(dnsamp$Fin2)

# Cubed response 
dnsamp$Fin3 <- ((dnsamp$FinCorrect)^3)
#hist(dnsamp$Fin3)
```


# Analyses
## Descriptives
```{r}
descriptives<-dnsamp%>%
  group_by(DNCondition)%>%
  summarise(MeanFinCorrect=mean(FinCorrect),
            se = sd(FinCorrect)/sqrt(length(FinCorrect)))
descriptives
```


## Model 1
Q: Does condition predict # of correct responses?
NOTE: Outcome variable is squared, so interpretation of the coefficients is tricky and they may look crazy! 
```{r}
Model_1<-lm(Fin2~DNCondition, data=dnsamp)    # Using squared outcome variable
mcSummary(Model_1)
# plot(Model_1)                               # Check assumptions again
```

# Exploratory Analyses
Q: Did Age predict children's accuracy? Did age interact with condition?
```{r}
Model_2_Age<-lm(Fin2~DNCondition*AgeYears, data=dnsamp) 
mcSummary(Model_2_Age)
#plot(Model_2_Age)

# Age * Condition interaction was redundant with condition (tol = 0.007), so it was removed to resolve multicollinearity (tol = .10 recommended for minimum tolerance;Tabachnick & Fidell, 2001; also see Daud, 2017; Slinker & Glantz 1985).


Model_3_Age<-lm(Fin2~DNCondition+AgeYears, data=dnsamp)  
mcSummary(Model_3_Age)
#plot(Model_3_Age)
```


#Plot
```{r}
#Prep data set for graphing
graphdf<-dnsamp%>%                                                   # Create new data set for graphing
  mutate("Condition" = ifelse(DNCondition == 0, 'Control',           # Relabel our contrasts to match our conditions in the paper
                             ifelse(DNCondition == 1, 'Delay', NA)), 
         Condition = as.factor(Condition)#,                          # Make sure condition is the right type (factor)
        # Age = round(AgeYears, digits=1),                           # Round age to a whole number 
        # Age = case_when(Age>=3.5 & Age <= 3.9 ~ "3.5-3.9",
        #                 Age>=4.0 & Age <= 4.4 ~ "4.0-4.5",
        #                 Age>=4.5 & Age <= 4.9 ~ "4.5-5.0")
         )%>%
  group_by(Condition)%>%                                             # Group the data set by condition  
  # summarize the data
  summarise(meanCorrect=mean(FinCorrect),                            # get group means
            n=length(FinCorrect),
            sd=sd(FinCorrect),
            se = sd/sqrt(n))                                         # get group SE
```

```{r}
plot1<-ggplot(graphdf,aes(Condition,meanCorrect, fill=Condition))+
  geom_bar(stat = 'identity', color='black', position = position_dodge())+
  geom_errorbar(aes(ymin=meanCorrect-se, ymax=meanCorrect + se), width=.2,
                  position=position_dodge(.9)) + 
  ggtitle("Average Number of Correct Trials in Delay and Control Conditons") +
  ylab("Average Numner of Correct Trials")+
  xlab("Day-Night Stroop Condition")+
  scale_fill_manual(values=c("gray91", "gray20")) +
  ylim(0,16)+
  theme(
    panel.background = element_rect(fill = "transparent"), # bg of the panel
    plot.background = element_rect(fill = "transparent", color = NA), # bg of the plot
    panel.grid.major = element_blank(), # get rid of major grid
    panel.grid.minor = element_blank(), # get rid of minor grid
    legend.background = element_rect(fill = "transparent"), # get rid of legend bg
    legend.box.background = element_rect(fill = "transparent"), # get rid of legend panel bg
    legend.key = element_rect(fill = "transparent", colour = NA), # get rid of key legend fill, and of the surrounding
    axis.line = element_line(colour = "black"), # adding a black line for x and y axis
    plot.title = element_text(hjust = 0.9)
  )
  
plot1

# save plot
ggsave(plot1, filename = "DN_acc_plot.png",  bg = "transparent")
```